Generating the Blueprints of Java Ecosystem

### 2015-02-22 msr.tex
updated msr.tex
added valid jars

All versions were filtered out and only the latest was kept. For each version in the Maven repository, each binary {\sc jar} file is accompanied by another {\sc jar}, which contains the source code. Table \ref{tbl:oss-size-metrics} presents several size metrics regarding the final version corpus. It included 12,959 projects, with more than 110 million lines of code.

\begin{table}
\centering
\caption{The selected Maven projects' size metrics}
\label{tbl:oss-size-metrics}
\begin{tabular}{l r}
 \hline
\textbf{Metric} & \textbf{Value}\\
\hline
Project Count & 12,959\\
File Count & 604,821\\
Module Count & 72,302\\
Lines of Code & 110,156,703\\
Source Lines of Code & 61,246,807\\
Comment Lines of Code & 36,696,217\\
Number of Classes & 499,588\\
Number of Interfaces & 89,145\\
Number of Enumerations & 12,732\\
\hline
\end{tabular}
\end{table}

@@

Table~\ref{tbl:selected-metrics} presents the key metrics that are calculated and stored in the dataset. Each tool focuses on a different aspect of a software system; \textit{ckjm} focuses on object-oriented design metrics, \textit{jdepend} on package design, while \textit{clmt} focuses on program size metrics. Several metrics are calculated by more than one tools in this dataset, like \textit{cyclomatic complexity}, which is calculated by both \textit{clmt} and \textit{ckjm}. Both calculation are stored and provided by the dataset. Three tools were selected.

>>>>

All versions were filtered out and only the latest was kept. For each version in the Maven repository, each binary {\sc jar} file is accompanied by another {\sc jar}, which contains the source code. Table \ref{tbl:oss-size-metrics} presents several size metrics regarding the final version corpus. It included 12,959 projects, with more than 110 million lines of code. Overall the dataset contains almost 33 million unique measurements.

\begin{table}
\centering
\caption{The selected Maven projects' size metrics}
\label{tbl:oss-size-metrics}
\begin{tabular}{l r}
 \hline
\textbf{Metric} & \textbf{Value}\\
\hline
Project Count & 11,365\\
File Count & 604,821\\
Module Count & 72,302\\
Lines of Code & 110,156,703\\
Source Lines of Code & 61,246,807\\
Comment Lines of Code & 36,696,217\\
Number of Classes & 499,588\\
Number of Interfaces & 89,145\\
Number of Enumerations & 12,732\\
Measurement Count & 32,844,836\\
\hline
\end{tabular}
\end{table}

@@

Table~\ref{tbl:selected-metrics} presents the key metrics that are calculated and stored in the dataset. Each tool focuses on a different aspect of a software system; \textit{ckjm} focuses on object-oriented design metrics, \textit{jdepend} on package design, while \textit{clmt} focuses on program size metrics. Several metrics are calculated by more than one tools in this dataset, like \textit{cyclomatic complexity}, which is calculated by both \textit{clmt} and \textit{ckjm}. Both calculation are stored and provided by the dataset.Three tools were selected.
